---
title: "SNSNETWORK"
author: "Vas and DEON"
date: '2022-07-19'
output: html_document
---
Packages SETUP
```{r echo=FALSE, warning=FALSE, error=FALSE}
#install.packages("bootnet")
#install.packages("networktools")
#install.packages("NetworkComparisonTest")
#install.packages("qgraph")
#install.packages("psych")
#install.packages("tidyverse")
#install.packages("semTools")
#install.packages("psychotools")
#install.packages("semPlot")
#install.packages("haven")
library(bootnet)
library(networktools)
library(NetworkComparisonTest)
library(qgraph)
library(psych)
library(psychotools)
library(tidyverse)
library(semTools)
library(semPlot)
library(haven)
```
Import Data
```{r error=FALSE, echo=FALSE, warning=FALSE}
dataset1 <- read_sav("Time Point 1.sav")
View(dataset1)

describe(dataset1)


```
Name Nodes
```{r echo=FALSE, error=FALSE, warning=FALSE}
names1 <- c("Salience", "Tolerance", "Mood Modification", "Relapse", "Withdrawal", "COnflict", "Depression1", "Anxiety_1", "Stress1")


```
Estimate Network
```{r echo=FALSE, warning=FALSE, error=FALSE}

network1 <- estimateNetwork(dataset1, default="EBICglasso")

```
Grouping nodes
```{r echo=FALSE, warning=FALSE, error=FALSE}
#group DASS and BSMAS nodes
groups1=list("SMA"=c(1:6), "Distress"=c(7:9))

```

Estimate Network Stability by bootstrapping network
```{r echo=FALSE, error=FALSE, warning=FALSE}
#Default Bootstrapping
b1 <- bootnet(network1, boots=1000, statistics=c("strength", "expectedInfluence", "edge"))
#Case Dropping Bootstrapping
b2 <- bootnet(network1, boots=1000, type="case", statistics=c("strength", "expectedInfluence", "edge"))


```

Get centrality stability coefficient
```{r echo=FALSE, error=FALSE, warning=FALSE}
corStability(b2)
```
Stability of the Network Plotting
```{r}

pdf("CentrStability1.pdf")
plot(b2)
dev.off()


```

Strength Centrality Diff Test, saved as pdf
```{r}
pdf("CentralityDifference1.pdf")
plot(b1, "strength", order="sample", labels=TRUE)
dev.off()
```


```{r echo=FALSE, error=FALSE, warning=FALSE}
pdf("EdgeStability1.pdf")
plot(b1, labels = FALSE, order = "sample")
dev.off()
```
Edge weights stability test saved as pdf
```{r echo=FALSE, error=FALSE, warning=FALSE}

pdf("EdgeDifftest1.pdf")
plot(b1, "edge", plot="difference", onlyNonZero=TRUE, order = "sample")
dev.off()


```

Plotting 

```{r echo=FALSE, error=FALSE, warning=FALSE}
pdf("plot1.pdf")
plot1 <- plot(network1, layout="spring", vsize=6, border.color="black", groups=groups1, color=c('lightblue', 'orange'))
dev.off()

```


create centrality plot and save as pdf

```{r echo=FALSE, error=FALSE, warning=FALSE}
pdf("CentralityPlot1.pdf", width=5)
c1 <- centralityPlot(plot1)
dev.off()
```

Inspect Centrality Indices
```{r echo=FALSE, warning=FALSE, error=FALSE}
Centrality1 <- centralityTable(network1)
write.csv(Centrality1, "Centrality1.csv")
view(Centrality1)

```
get the edges strength/ correlations
```{r echo=FALSE, error=FALSE, warning=FALSE}

edges1<-getWmat(network1)
write.csv(edges1, "edges1.csv")

```

Estimate the Bridge Values
```{r echo=FALSE, error=FALSE, warning=FALSE}

bridge1<-bridge(plot1, communities=c('1', '1', '1', '1', '1', '1', '2', '2', '2'), useCommunities = "all", directed = NULL, nodes = NULL)
view(Bridges)

```

Plotting Bridges Strength
```{r}
pdf("bridgecentrality1.pdf", width = 5)
plot(bridge1, include = "Bridge Strength")
dev.off()


```


